Wealth Inequality in China: Evidence from the 2017 and 2019 CHFS

### 2025-04-05 first_draft/draft.qmd
updtae

@@

## Group decomposition of wealth inequality by rural and urban
This section presents the group decomposition of wealth inequality by the urban-rural and regional divisions.

| Group | Population Share | Mean | Relative Mean | Median Income | Wealth Share | Gini |
|-------|-----------------|------|---------------|---------------|--------------|------|
| 2017 Urban | 0.6235 | 1,146,510 | 1.3665 | 66,760 | 0.8521 | 0.6573 |
| 2017 Rural | 0.3765 | 329,715 | 0.3930 | 23,660 | 0.1479 | 0.6945 |
| 2019 Urban | 0.6500 | 1,461,675 | 1.3464 | 69,600 | 0.8752 | 0.6165 |
| 2019 Rural | 0.3500 | 387,130 | 0.3566 | 27,541 | 0.1248 | 0.6629 |

@@

Notably, the Gini coefficient for wealth is higher in rural areas than in urban areas in both 2017 and 2019.

@@

>>>>

Notably, the growth rate of mean and median income from 2011 to 2017 is clearly higher than that of wealth but from 2017 to 2019, the growth of mean and median wealth surpasses that of income by a great margin.

@@

## Group decomposition of wealth inequality by rural and urban
The following two sections present the group decomposition of wealth inequality by the urban-rural and regional divisions.

| Group      | Sample Share | Mean    | Relative Mean | Median Income | Wealth Share | Gini |
|------------|--------------|---------|---------------|---------------|--------------|------|
| 2017 Urban | 0.6235 | 1,146,510 | 1.3665 | 66,760 | 0.8521 | 0.6573 |
| 2017 Rural | 0.3765 | 329,715 | 0.3930 | 23,660 | 0.1479 | 0.6945 |
| 2019 Urban | 0.6500 | 1,461,675 | 1.3464 | 69,600 | 0.8752 | 0.6165 |
| 2019 Rural | 0.3500 | 387,130 | 0.3566 | 27,541 | 0.1248 | 0.6629 |

@@

Notably, the Gini coefficient for wealth is higher in rural areas than in urban areas in both 2017 and 2019. The Gini coefficient for both urban rural areas declined from 2017 to 2019.

@@

| Region         | Sample Share | Mean        | Relative Mean | Median Income | Wealth Share | Gini   |
|----------------|--------------|-------------|---------------|---------------|--------------|--------|
| 2017 East     | 0.3754       | 1,391,421   | 1.6584        | 556,993       | 0.6226       | 0.6747 |
| 2017 Middle   | 0.2659       | 550,976     | 0.6567        | 272,235       | 0.1746       | 0.6648 |
| 2017 West     | 0.2628       | 496,937     | 0.5923        | 252,341       | 0.1556       | 0.6569 |
| 2017 Northeast| 0.0960       | 412,387     | 0.4915        | 212,512       | 0.0472       | 0.6513 |
| 2019 East     | 0.3987       | 1,658,323   | 1.5276        | 760,140       | 0.6090       | 0.6305 |
| 2019 Middle   | 0.2651       | 677,697     | 0.6243        | 372,434       | 0.1655       | 0.5997 |
| 2019 West     | 0.2400       | 799,535     | 0.7365        | 343,542       | 0.1768       | 0.6947 |
| 2019 Northeast| 0.0962       | 549,715     | 0.5064        | 291,085       | 0.0487       | 0.6369 |

The above summary statistics shows that the mean and median wealth in the East is significantly higher than in the other regions in both 2017 and 2019. Notably, the mean and median wealth of the West-area households surpassed that of the Middle in 2019, but West's Gini coefficient rose to the highest among all regions in 2019 as well.

The decomposition of the Gini coefficient into within-group, between-group, and residual components shows:

| Year | Total Gini | Within-group | Between-group | Residual |
|------|------------|--------------|---------------|----------|
| 2017 | 100.00 | 31.16 | 36.88 | 31.96 |
| 2019 | 100.00 | 31.69 | 33.77 | 34.54 |

The group decompsition shows that similar to the urban-rural decomposition, the between-group component contribues over 30% to the overall wealth inequality in both 2017 and 2019. The between group contribution saw a slight decrease from 2017 to 2019 with a similari increase in the residual component. This might signal some modest convergence in household wealth between regions.
